---
title: Phyllotaxis Project
author: Mike Page
date: '2018-09-06'
slug: phyllotaxis-project
categories: []
tags: []
description: Desc
hacker_news_id: ''
lobsters_id: ''
meta_img: /images/image.jpg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = "center")
```

<span style="color:grey">Michael Page</span>
<br/>


### INFO

This post isn't so much a 'blog' post as it is a repository for me to store my code for the 'Phyllotaxis: Draw flowers using mathematics' project which can be found on [DataCamp](https://www.datacamp.com/projects/62). Most of the code follows the standard solutions for the project, with the exception of using theme_void() to remove elements from a plot. Using theme_void() is a more elegant solution, in this case, than independetly assigning element_blank() to each element (e.g, panel.grid, axis.title, axis.text.y, etc.)!


***

```{r}
library(ggplot2)

options(repr.plot.width = 4, repr.plot.height = 4)

t <- seq(0, 2*pi, length.out = 50)
x <- sin(t)
y <- cos(t)
df <- data.frame(t, x, y)

# Make a scatter plot of points in a circle
p <- ggplot(df, aes(x, y))
p + geom_point()

# Defining the number of points
points <- 500

# Defining the Golden Angle
angle <- pi*(3-sqrt(5))

t <- (1:points) * angle
x <- sin(t)
y <-cos(t)
df <- data.frame(t, x, y)

# Make a scatter plot of points in a spiral
p <- ggplot(df, aes(x*t, y*t))
p + geom_point()

df <- data.frame(t, x, y)

# Make a scatter plot of points in a spiral
p <- ggplot(df, aes(x*t, y*t))
p + geom_point() +
theme_void()

# Add colour, size, and transparency to plot

p <- ggplot(df, aes(x*t, y*t))
p + geom_point(size = 8, alpha = 0.5, color = "darkgreen") +
theme_void()

# Map size to variable t and move legend

p <- ggplot(df, aes(x*t, y*t))
p + geom_point(aes(size = t), alpha = 0.5, color = "black", shape = 8) +
theme_void() +
theme(legend.position="none")

# Plot sunflower

p <- ggplot(df, aes(x*t, y*t))
p + geom_point(aes(size = t), alpha = 0.5, color = "yellow", shape = 17) +
theme_void() +
theme(legend.position="none", plot.background = element_rect(fill = "darkmagenta"))

# Changle angle from golden angle (aprrox 2.4) to 2.0
angle <- 2
points <- 1000

t <- (1:points)*angle
x <- sin(t)
y <- cos(t)

df <- data.frame(t, x, y)

p <- ggplot(df, aes(x*t, y*t))
p + geom_point(aes(size = t), alpha = 0.5, color = "yellow", shape = 17) +
theme_void() +
theme(legend.position="none", plot.background = element_rect(fill = "darkmagenta"))

# Final plot

angle <- 13*pi/180
points <- 2000

t <- (1:points)*angle
x <- sin(t)
y <- cos(t)

df <- data.frame(t, x, y)

p <- ggplot(df, aes(x*t, y*t))
p + geom_point(aes(size = t), alpha = 0.1, color = "magenta4", shape = 1, size = 80) +
theme_void() +
theme(legend.position="none")
```

